%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

%%
%%

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%https://www.overleaf.com/12940811gwwnrnjkzqtq#%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://github.com/raghunanj/}{\Large Raghunandana Jayarama Reddy}} & \Email \href{mailto:rnjreddy93@gmail.com}{ rnjreddy93@gmail.com}\\
  \textbf{\href{http://www.raghunanj.com/}{http://www.raghunanj.com/}} & \Mobilefone{ +1-(530) 603-1196} \\
\end{tabular*}

%


  

%-----------EXPERIENCE-----------------
\section{Experience \hfill \faLinkedin \href {https://www.linkedin.com/in/raghunanj/}{ raghunanj}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Juniper Networks Inc }{Sunnyvale, CA}
      {Software Engineer Intern, Enterprise Data Platform}{May 2018 - Present}
      \resumeItemListStart
      \resumeItem{Data Integration/Migration}
      {I implemented backend code for transformation, aggregation \& co-relation of data(ETL) between the data store(snowflake), Storage(AWS S3) \& the Analytics layer(AWS EMR Spark).}
      \resumeItem{Predictive Analytics model}
      {I developed a predictive analytics model for forecasting the sales revenue data on the EMR Spark cluster using Spark MLib framework, fbProphet \& Apache Zeppelin for visualization.\textbf{\href{https://www.dropbox.com/s/3w3qwmne5uv8epf/FinalPosterRaghu.pdf?dl=0}{(Poster)} }}
      \resumeItemListEnd
  

    \resumeSubheading
      {Juniper Networks Inc }{Bengaluru, India}
      {Software Engineer 2, Internal Core Apps - Platform}{Jul 2015 - Jun 2017}
      \resumeItemListStart
        \resumeItem{Ignition}
          {I worked on backend development(API and features) for a SaaS platform release for data management   \& redesigned it\'s query handling \& scaled down the performance factor by atleast 30\% for the end user.}
        \resumeItem{Vesper}
          {I designed \& developed the enhancements for a data cleansing platform release. }
      \resumeItemListEnd

    \resumeSubheading
      {Juniper Networks Inc}{ Bengaluru, India}
      {Software Engineer Intern, IT Applications management}{Jan 2015 - Jun 2015}
      \resumeItemListStart
        \resumeItem{Ignition} {I designed and implemented the automation suite for few End-to-End tasks \& ensured that the performance and optimality of the designed solution are meeting a logical end by building a simulator.}  
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  

  %--------PROGRAMMING SKILLS------------
\section{Programming Skills}
%   \resumeSubHeadingListStart
    
      \textbf{Languages}{:  Python, C, C++, Java, MySQL, JavaScript, Go, Scala. } \hfill \textbf{OS}{: OSX, Linux, FreeBSD, Windows}
      
      \textbf{Infrastructure/Platform}{: Amazon Web Services, Git, Spark, Cassandra, Docker, Snowflake, Kinesis/Kafka. }
       
       \textbf{Technologies}{: OpenCV, SkLearn, Pandas, Scipy, Keras, Tensor-flow, PyTorch, PySpark, AWS CLI. }
    
%   \resumeSubHeadingListEnd







%-----------PROJECTS-----------------
\section{Selected projects \hfill \textbf{\href{https://github.com/raghunanj/}{https://github.com/raghunanj/}}}
  \resumeSubHeadingListStart  
      \resumeSubItem{SBUnix}{A 64 bit OS with shell, tarfs, COW fork, virtual memory, syscalls and binaries support.  } 
      \resumeSubItem {\textbf {\href{https://github.com/raghunanj/ComputerVisionBasics}{VisionMetrics}}}{An archive of code and projects involving Blending, Image Alignment, Detection \& Tracking, \textbf{\href{https://www.youtube.com/watch?v=39CRobb2uGQ}{Segmentation }}\& Structured light.}
  \resumeSubItem{Cross-Modality Convolution for 3D Biomedical Segmentation}
      {A deep encoder-decoder structure with cross-modality convolution layers to incorporate different modalities of MRI data implemented using convolution LSTMs in Tensorflow.} 
      \resumeSubItem{NetSec tools}
      {A plugboard proxy for adding an extra layer of protection to publicly accessible network services and an on-path DNS packet injector and a passive DNS poisoning attack detector.}
      \resumeSubItem{Extending serialization protocols}{\textbf{Google Summer of Code } participant worked with the Apache Dubbo community in extending the serialization protocols using protobuf. }
      
   

       \resumeSubItem{Blogger Android app}
      {Developed a blogger andorid app for users to categorize their favorite blog articles based on their interests.}
     
   
      
     
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stony Brook University, State University of New York}{Stonybrook, NY}
      {Master of Science in Computer Science;   }{Aug. 2017 -- (expected) Dec. 2018}
\begin{itemize}
\item Coursework: Analysis of Algorithms,  Operating Systems, Network Security, Probability \& Statistics for Data Science, Computer Vision, Convex Optimization algorithms, Asynchronous distributed systems.
\end{itemize}
    \resumeSubheading
      {PES Institute of Technology}{Bengaluru, India}
      {Bachelor of Engineering in Computer Science;  GPA: 8.93/10.0}{Aug. 2011 -- July. 2015}
      \begin{itemize}
\item Coursework: Analysis and Design of Algorithms, Computer Networks, Unix Programming, Fuzzy logic, Compiler Design, Principles of Programming Languages, Intro to Web Technologies, Database systems. 
\end{itemize}
  \resumeSubHeadingListEnd


%--------AWARDS&HONORS------------
\section{AWARDS \& HONORS}  
\begin{itemize}[noitemsep]

\item {Incredible Talent Team award in 2016-2017 at Juniper Networks Inc India.}
\item {1st Runner Up in the Intuit Android hackathon and an active participant in hackathons. }
\end{itemize}
  

%-------------------------------------------
\end{document}
